PK object batch mode trial

### 2023-07-10 data-raw/batchMode_trial_gpm.Rmd
Completed the logLik, AIC and BIC methods for the pk object.

my_predata <- subset(cvt,
                     chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                                   "DTXSID2021731",
                                                                   "DTXSID5032600"))
```

@@

```{r single_fit}
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference))

@@

my_coefs_update <- coef(my_pk)
my_pred_update <- predict(my_pk,
                          exclude = TRUE, # add the "exclude" column to output
                          use_scale_conc = TRUE)

@@

```{r remaining_methods}
# coef_sd
# logLik.pk
# get_tkstats()
devtools::load_all()
get_tkstats(my_pk) %>% head()
get_tkstats(my_pk) %>% View("TK_test")
my_tkstats <- get_tkstats(my_pk)

# For the July 5th version where it returns a nested dataframe
# 
my_tkstats %>%
  reframe(tkstats_df = purrr::map(c_data,
                                  \(x) {
                                    x %>%
                                      dplyr::rowwise() %>%
                                      dplyr::mutate(
                                        TKstats = sapply(
                                          coefs_vector,
                                          FUN = tk_fun,
                                          route = Route,
                                          medium = Media,
                                          dose = Dose,
                                          time_unit = Time.Units,
                                          conc_unit = Conc.Units,
                                          vol_unit = "L",
                                          simplify = FALSE,
                                          USE.NAMES = TRUE
                                        )
                                      ) %>%
                                      dplyr::ungroup()
                                  })) -> my_tkstats

my_tkstats %>% unnest(cols = c(tkstats_df)) -> my_tkstats

my_tkstats %>% mutate(TKstats_wide  = map(TKstats,
                                     \(x) {
                                       dplyr::select(x, -param_units) %>%
                                         tidyr::pivot_wider(names_from = param_name,
                                                     values_from = param_value)
                                     })) %>%
  unnest(cols = c(TKstats_wide)) %>% View()

@@

>>>>

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                              "DTXSID5032600"))

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID3061635"))

@@

```{r single_fit}
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

@@

my_coefs_update <- coef(my_pk, drop_sigma = TRUE)
my_pred_update <- predict(my_pk,
                          exclude = TRUE, # add the "exclude" column to output
                          use_scale_conc = TRUE)

@@

```{r get_tkstats_logLik_methods}
my_tkstats <- get_tkstats(my_pk)

names(my_tkstats)
my_tkstats

my_logLike_update <- logLik(my_pk)

@@

```{r remaining_methods}
# coef_sd
# logLik.pk

devtools::load_all()
AIC(my_pk)
BIC(my_pk)

The purpose of the following code is to generate data.frames with information for
all 103 chemicals in the `cvt` dataset that comes with `invivopkfit`.
I will need to do append each dataframe to the last for the outputs of the following
methods:

- `AIC()`
- `BIC()` left-joined with `AIC` output
- `get_tkstats()`

I will also have to fit these iteratively and manage the memory as part of the loop.

```{r for_loop_allDTXSIDs}

# All DTXSID
eachDTXSID <- unique(cvt$chemicals_analyzed.dsstox_substance_id)

id <- 1
AIC_BIC <- data.frame()
while (id <= 10) {
  # Establishing the loop
  DTX_set <- eachDTXSID[seq(from = id, to = id + 3)]
  DTX_set <- DTX_set[!is.na(DTX_set)]
  print(DTX_set)
  id <- id + 4
  Sys.sleep(0.5)

  # Subsetting cvt
  my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% DTX_set)

  # Fitting loop
  my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species)) # Pooled model

  my_pk <- do_fit(my_pk)

  # OUTPUTS
  # AIC/BIC
  temp_AIC <- AIC(my_pk)
  temp_BIC <- BIC(my_pk)
  temp_IC <- left_join(temp_AIC, temp_BIC)
  AIC_BIC <- bind_rows(AIC_BIC, temp_IC)

} # Doesn't work because something for Solvent red 1 introduces an error
